### 2021-01-22 appendix.tex
Changed sec title
Made a bunch of minor changes?

% !TeX root = priorities.tex
\section{Priority GV}
\begingroup
\usingnamespace{pgv}

% Scheduler example
\input{fig/pgv-scheduler}

% Proofs that the syntactic sugar is well-typed.
\input{fig/pgv-typing-sugar}

\restatelemma{lempgvvaluedone}
\input{prf/lem-pgv-value-done}

@@

\restatetheorem{thmpgvclosedprogressconfs}
\input{prf/thm-pgv-closed-progress-confs}
\endgroup

@@

\input{fig/pcp-operational-semantics-and-typing}

\subsubsection*{Operational Semantics}
The operational semantics for PCP, given in \cref{fig:pcp-operational-semantics-and-typing}, is defined as a reduction relation $\pcp{\red}$ on processes (bottom) and uses structural congruence (top). Each of the axioms of structural congruence corresponds to the axiom of the same name for PGV. We write $\pcp{\red^+}$ for the transitive closures, and $\pcp{\red^\star}$ for the reflexive-transitive closures.

@@

\subsubsection*{Typing}
\Cref{fig:pcp-operational-semantics-and-typing} gives the typing rules for our version of PCP. A typing judgement $\pcp{\seq{P}{\Gamma}}$ states that ``process $\pcp{\tm{P}}$ is well typed under the typing context $\pcp{\ty{\Gamma}}$''.

@@

\subsection{Translation}
\begingroup
\restatelemma{lempcptopgvtermspreservation}
\input{prf/lem-pcp-to-pgv-terms-preservation}

>>>>

% !TeX root = priorities.tex
\section{Priority GV}
\begingroup
\usingnamespace{pgv}
\restatelemma{lempgvvaluedone}
\input{prf/lem-pgv-value-done}

@@

\restatetheorem{thmpgvclosedprogressconfs}
\input{prf/thm-pgv-closed-progress-confs}

\input{fig/pgv-typing-sugar}
\endgroup

@@

\subsubsection*{Operational Semantics}
The operational semantics for PCP, given in \cref{fig:pcp-operational-semantics}, is defined as a reduction relation $\pcp{\red}$ on processes (bottom) and uses structural congruence (top). Each of the axioms of structural congruence corresponds to the axiom of the same name for PGV. We write $\pcp{\red^+}$ for the transitive closures, and $\pcp{\red^\star}$ for the reflexive-transitive closures.

@@

\input{fig/pcp-operational-semantics}

\subsubsection*{Typing}
\Cref{fig:pcp-typing} gives the typing rules for our version of PCP. A typing judgement $\pcp{\seq{P}{\Gamma}}$ states that ``process $\pcp{\tm{P}}$ is well typed under the typing context $\pcp{\ty{\Gamma}}$''.

\input{fig/pcp-typing}

@@

\subsection{Correspondence between PGV and PCP}
\begingroup
\restatelemma{lempcptopgvtermspreservation}
\input{prf/lem-pcp-to-pgv-terms-preservation}
